Community-Conditioned Language Models

### 2020-11-08 paper/paper.tex
other potentially relevant paper

\paragraph{Language models for sociolinguistic variation}
- Del Tredici, M., & Fernández, R. (2017). Semantic Variation in Online Communities of Practice. https://www.aclweb.org/anthology/W17-6804
https://www.aclweb.org/anthology/W17-2904.pdf

>>>>

\paragraph{Reddit Mining to Understand Gendered Movements}
http://ceur-ws.org/Vol-2578/DARLIAP3.pdf

\paragraph{Language models for sociolinguistic variation}
\cite{DelTredici2017}
